*Supplementary Material 2*

### 2022-06-20 ms/si.Rmd
Fix formatting

```{r setup-si, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, results = 'hide')
# Load packages
library(ggupset)
library(flextable)
source(here::here("R/ms_packages.R"))
```

>>>>

```{r setup-si, include = FALSE}
knitr::opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, results = "hide",
  cache = FALSE)
# Load packages
library(ggupset)
library(flextable)
source(here::here("R/ms_packages.R"))
```

### 2022-06-20 ms/si2.Rmd
Fix formatting

```{r setup-rmd, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE, warning = FALSE, message = FALSE, results = 'hide')
library(glue)
library(gluedown)
library(tidyverse)
library(assertr)
```

@@

```{r load-captions-si2, cache = FALSE}
# Source captions numbers from MS
# 
# So that caption numbers are in order of appearance in MS

>>>>

```{r setup-rmd, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, include = FALSE,
  warning = FALSE, message = FALSE, results = "hide")
library(glue)
library(gluedown)
library(tidyverse)
library(assertr)
```

@@

```{r load-captions-si2, cache = FALSE}
# Source captions numbers from MS.
# So that caption numbers are in order of appearance in MS
